---
title: 'TidyTuesday 2022 Week 2: Bee Colonies'
author: "Jennifer Truong"
date: "1/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

#Load packages
library(tidyverse)
library(tidytuesdayR)
```

```{r Get data}
tuesdata <- tidytuesdayR::tt_load('2022-01-11')
colony <- tuesdata$colony
stressor <- tuesdata$stressor
```

Time to explore data!

# Data Dictionary

## colony.csv
variable 	class 	description
year 	character 	year
months 	character 	month
state 	character 	State Name (note there is United States and Other States)
colony_n 	integer 	Number of colonies
colony_max 	integer 	Maximum colonies
colony_lost 	integer 	Colonies lost
colony_lost_pct 	integer 	Percent of total colonies lost
colony_added 	integer 	Colonies added
colony_reno 	integer 	Colonies renovated
colony_reno_pct 	integer 	Percent of colonies renovated

## stressor.csv
year 	character 	Year
months 	character 	Month range
state 	character 	State Name (note there is United States and Other States)
stressor 	character 	Stress type
stress_pct 	double 	Percent of colonies affected by stressors anytime during the quarter, colony can be affected by multiple stressors during same quarter.

### Any interesting variables?
Probably the colony_lost, colony_added, and colony_reno. Could have done % variables, but I wonder why there's no % variable for colony added. Maybe group the states by region for easier viewieing

# Check for correlations
```{r}
library(corrr)
library(corrplot)

# Create subset only containing numeric variables
colony_select <- colony %>%
  select(colony_n, colony_max, colony_lost, colony_lost_pct, colony_added, colony_reno, colony_reno_pct)

# Create correlation matrix
colony_cor <- colony_select %>%
  correlate()

colony_cor
```

Strongest correlation seems to be between number of colonies, max number of colonies, and colonies lost. Colonies added and colonies renovated also seem to have strong correlation.

## Plot correlations
```{r}

rplot(colony_cor)
```

# How about if we pick a specific region?
```{r}
# Create vectors for East Coast and West Coast states
#eastcoast = ("Maine", "New Hampshire", "Massachusetts", "Rhode Island", "Connecticut", "New York", "New Jersey", "Delaware", "Maryland", "Virginia", "North Carolina", "South Carolina", "Georgia", "Florida")

# Subset states by East Coast and West Coast

# Create correlation matrix again

```

# Final variables to examine
year, state (group into region?), colony_n, colony_max, colony_lost, colony_added, colony_reno